Output Summary

### 2023-03-14 03-post-process/output-plots-children/04-egg-to-parr-surv.Rmd

## Survival Time Series

@@

>>>>

## Survival Time Series {.tabset .tabset-pills}

These figures show the realized time series of egg-to-parr survival that include all sources of variability in red: that explained by Beverton-Holt dynamics and that not explained by it.

### Realized Alone

Just the realized time series shown.

@@

### Realized & BH

The blue shows the time series with variability explained only by Beverton-Holt dynamics.

```{r phi_E_Pb_dot-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])

  # draw on the posterior time series that includes BH prediction only
  dot_col = "royalblue"
  dot = post_summ(post, sub_index("^phi_E_Pb_dot[year,pop]", pop = j, year = ts_yrs))
  polygon(x = c(all_yrs[ts_yrs], rev(all_yrs[ts_yrs])),
          y = c(dot["2.5%",], rev(dot["97.5%",])),
          col = scales::alpha(dot_col, 0.15), border = NA)
  lines(dot["mean",] ~ all_yrs[ts_yrs], col = dot_col, lwd = 2)
  lines(dot["2.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
  lines(dot["97.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
}

### Realized & [BH + AR(1)]

The blue shows the time series with variability explained by Beverton-Holt dynamics and the carry-over residual.

```{r phi_E_Pb_dot2-plots, fig.width = 6, fig.height = 5}
plot_f = function(j) {
  plot_tseries(post_summ(post, sub_index("^phi_E_Pb[year,pop]$", year = ts_yrs, pop = j)),
               yrs = all_yrs[ts_yrs],
               main = pops[j])

  # draw on the posterior time series that includes BH prediction and the carry over residual from last year
  dot_col = "royalblue"
  dot = post_summ(post, sub_index("^phi_E_Pb_dot2[year,pop]", pop = j, year = ts_yrs))
  polygon(x = c(all_yrs[ts_yrs], rev(all_yrs[ts_yrs])),
          y = c(dot["2.5%",], rev(dot["97.5%",])),
          col = scales::alpha(dot_col, 0.15), border = NA)
  lines(dot["mean",] ~ all_yrs[ts_yrs], col = dot_col, lwd = 2)
  lines(dot["2.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
  lines(dot["97.5%",] ~ all_yrs[ts_yrs], col = dot_col, lty = 2)
}

### 2023-03-14 03-post-process/output-plots-children/11-param-summaries.Rmd

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,4))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```

>>>>

```{r recruit-bxp, fig.width = 8, fig.height = 3.5}
par(mfrow = c(1,5))
my_boxplot("^alpha[.]$", "Productivity")
my_boxplot("^beta[.]$", "Capacity")
my_boxplot("^sig_Lphi_E_Pb[.]$", "Process SD")
my_boxplot("^kappa_phi_E_Pb[.]$", "AR(1) Coef.")
my_boxplot("^rho_Lphi_E_Pb", "Among-pop Correlation", ticklabs = vcov_labels, las = 3)
```
